Reconstructing the Lensing Mass in the Universe \\ from Photometric Catalog Data

### 2012-10-30 doc/paper-lcr.tex
more intro in hilbert 2011 etc, MS section added

Every distant object we observe has had its apparent shape distorted,
and size and total brightness magnified (or demagnified) by a compound
weak gravitational lens constructed from all the mass distributed
between us and it. As \citet{Vale+White2003} and \citet{HilbertEtal2007}
showed, there are no empty lines of sight through our universe. This
fact makes gravitational lensing a potentially important source of
systematic error for any estimate of luminosity (or distance), an issue
raised for \eg type Ia supernovae by
\citet[][]{Holz+Wald1998,Linder+Holz2004}, for gamma ray bursts by
\citet[][]{Oguri+Takahashi2006,Wang+Dai2011},  and for high redshift
galaxies by \citet{BradacEtal2009}, among others.

@@

Several attempts have been made to do better than simply constructing a
large sample of objects, and averaging over the resulting convergence
distribution. The weak lensing effect can be detected by measuring the
small distortions it induces on the images of many background galaxies
in the field \citep[see e.g.][for a review]{SaasFee2006}. In a 30''
radius aperture around the strong lens Q0957$+$561,
\citet{NakajimaEtal2009} used deep HST imaging to measure a weak lensing
convergence of $0.17/pm0.06$, which was used in the time delay distance
measurement of \citep{FadelyEtal2009}. While this system has an
unusually high external convergence due to its location on the edge of a
cluster of galaxies, the precision with which the convergence at the
lens position can be estimated is indicative of what can be achieved
with high quality weak lensing shear data. We note that this uncertainty
is not dependent on the value of the convergence, but instead depends
primarily on the number density of weakly lensed, measurable galaxies
available.

@@

The probability density function (PDF) for the external convergence
given our available data $\data$, $\Pr(\xkappa|\data)$,  is the  key
quantity we seek, since by marginalising over this distribution we can
correctly propagate the uncertainties due to line-of-sight perturbations
(as \citeauthor{FadelyEtal2009} did).
\citet{WongEtal2011} came close to estimating this quantity from their
survey data, running Monte Carlo reconstructions of the mass in nine
lens fields based on \citeauthor{WilliamsEtal2006} and
\citeauthor{MomchevaEtal2006}'s photometric and spectroscopic
measurements of galaxies close to the line of sight, and comparing the
resulting predicted shear distributions with the external shear demanded
by the strong lens model. Their reconstructions showed most of the shear
to have been generated by bright galaxies within 2~arcminutes of the
lens, and that both line of sight structures and the group of galaxies
in each lens plane contribute significant proportions of the shear. They
found significant discrepancies between the lens model shear and the
Monte Carlo predictions, but were unable to distinguish between the
environment modelling and the strong lens modelling as the cause of
these discrepancies.

These observational investigations have provided some very useful
insight into the problem of convergence estimation.  Coming from a more
theoretical direction, large numerical simulations have been used to
predict, from first principles, the distribution of likely external
shears and convergences along various lines of sight, including those
containing strong lens systems.  \citet{Holder+Schechter2003} and
\citet{DalalEtal2005} carried out ray-tracing calculations in N-body
simulations to estimate the distribution of external shear values. 
\citet{HilbertEtal2009} performed similar ray-tracing experiments
through the Millenium Simulation \citep{SpringelEtal2005}, generating a
predicted $\kappa$ at every position in a simulated sky.
\citet{HilbertEtal2009} found that \MS lines of sight with strong lenses
were not biased towards high $\kappa$, although selection functions for
discovering or using particular samples of strong lenses were not taken
into account. The first step towards using this excellent calibration
resource was taken by \citet{SuyuEtal2010}, who selected \MS lines of
sight by their apparent galaxy overdensity, in a 45 arcsec radius
aperture down to $i < 24.5$, to match the observed overdensity towards
the time delay lens B1608$+$656 \citep{FassnachtEtal2011}. The resulting
distribution of $\kappa$ values from the ray-tracing was taken to be an
estimate of  $\Pr(\kappa)$. B1608$+$656 is indeed a high $\kappa$ line
of sight, but it does not reside in a massive cluster environment. In a
companion paper to this one, \citet{GreeneEtal2012} investigated
improvements to this method by weighting the galaxy counts by galaxy
mass, and perpendicular distance to the line of sight, again using the
\MS mock catalogs and their associated $\kappa$ values to construct
$\Pr(\kappa|\data)$.

In this paper, we combine the halo model reconstruction approach of
\citeauthor{WongEtal} and others with the idea of calibrating to
simulations from \citeauthor{SuyuEtal2009} in order  to build a
framework for bringing all available information to bear on the problem
of estimating the weak the lensing convergence due to mass along the
line of sight to a distant source.  Taking the $\kappa$ values from
\citeauthor{HilbertEtal2009}'s ray-tracing calculations as the ``truth''
that we have to recover, we use the \MS mock galaxy catalogs to test the
accuracy of line of sight mass reconstruction. Probabilistically
assigning mass and redshift to every observed galaxy in a given observed
field, we generate Monte Carlo sample line of sight mass distributions,
and so construct the PDF $\Pr(\kappa|\data)$.  We aim to answer the
following questions:

@@

\item We have some choices to make when planning follow-up observations
of interesting sightlines. How should we select objects to achieve the
highest accuracy convergence reconstruction, and hence the highest
accuracy global parameter estimates?

@@

\begin{figure*}
\includegraphics[width=\textwidth]{figs/viewofalightcone.eps}
\caption[magcut]{4 different views of a lightcone around a typical line
of sight. This line of sight is slightly overdense with a $\kappa$ of
0.03. Top left show the positions of galaxies, the area of the circles
is proportional to observed $i$-band flux; the brightest object shown
has an $i$ magnitude of 17.7. Top Centre show the angular sizes of halos
on the sky; red regions are within the NFW scale radius of a halo and
blue shows the virial radius of each halo - there are clearly no empty
lightcones. Top right shows the individual $\kappa$ contributions of
each halo, assuming the \citet{BMO} profile and the \citet{Neto2007}
mass-concentration relation. Bottom a view along the redshift axis,
showing only halos with $|x|<0.3$ arcmin; the area of the points is
scaled by halo mass; the most massive halo shown has
$1.6\times10^{12}\Msun$; the optical axis is the dashed line whilst the
dotted lines are the lens and source planes for a B1608-like strong
lens.}
\label{fig:lightcone}
\end{figure*}

@@

Convergence, or Ricci focusing, occurs when a gravitational lens focuses the rays in a raybundle.
This focussing can cause distant objects to appear brighter, and larger than they would if the lens
 were removed.
The convergence from an isolated mass sheet is the ratio of the projected surface mass density
($\Sigma(D_{\mathrm{od}}\bmath{\theta})$) devided by the critical surface mass density at the redshift of the mass sheet ($\Sigma_{\rm cr}$),
\be
\kappa(\bmath{\theta})= \frac {\Sigma(D_{\mathrm{od}}\bmath{\theta})}{\Sigma_{\rm cr}(z)}
\ee
where 
\be \label{eq:sigcrit} 
\Sigma_{\rm cr}(z) \equiv \frac{c^2 D_{\rm os}}{4 \pi G D_{\rm od} D_{\rm ds}}.
\ee
and the D's are the angular diameter distances between the objects refered to in the subscripts: o is the observer, d is the deflector and s is the source. If the surface mass density of the sheet exceeds $\Sigma_{\rm cr}$, multiple images of the source can
occur, otherwise only one image will be observed, although that image will still be perturbed
relative to the unlensed case.

@@

Strong lenses sit in our real Universe -- they are not truely isolated;
there is some mass along the line of sight coming from intervening structures.
These structures may be physically associated with the lens e.g. other members
of a group or cluster, or they may be the result of chance alignments at any redshift. 
Whilst it is rare for three galaxies to line up well enough for both of the background sources
to be strongly lensed \citep{GavazziEtal2008,CollettEtal2012a}, the shear scale of dark matter halos
makes a partial alignment -- with the additional structure acting as a perturbing weak lens -- 
a near certainty \citep{Vale+White2003,HilbertEtal2007}. These additional
structures induce an external shear which can be recovered in the mass-modelling
of the lens, but they can also introduce a convergence that
is undetectable from the image positions, shapes and relative fluxes; {\it the
mass sheet-degeneracy} \citep{FalcoEtal1985}.

If the intrinsic source brightness changes, the observed brightness in each image does not change
simultaneously - there is a time delay, $\Delta t$, between the brightness change in
each image. Despite the invariance of the image positions and fluxes, under the addition
of an external convergence (and appropriate re-scaling of the lens potential) the relative Fermat potential between the images is {\it not}
invariant, and so the time delay changes. As such it is necessary to include $\kappa$
in the lens modelling, if cosmological parameters are to be estimated accurately and
precisely from observed time delays \citep{SuyuEtal2010}. If there is any external convergence, that is not included in the lens
modeling, then the time delay distance -- inferred assuming $\kappa = 0$ -- will be
$(1-\kappa)$ less than the true value of $\Dt$.
\be 
\label{eq:MassSheet:Dtbias}
\Dt^{\rm{true}}=(1-\kappa) \Dt^{{\kappax = 0}}.
\ee
We can overcome this degeneracy with additional knowledge of $\kappa$.
Since $\kappa$ is typically small the absolute uncertainty on the estimate
of $\kappa$ correspends to the percentage uncertainty with which time-delay
distances can be infered.

For mass-sheets that are physically associated with the lens galaxy, the mass sheet
 affects the stellar dynamics of the
lens galaxy, so dynamical observations can break the internal
mass-sheet degeneracy by providing an additional estimate of the lens galaxy's mass
\citep[e.g.,][]{SuyuEtal2010}. In this work our aim is to quantify the lensing effect of mass-sheets that are not physically associated with the lens galaxy -- mass-sheets
lying infront or behind the lens -- and the uncertainties induced by reconstructing
those mass-sheets using simple prescriptions applied to potential astronomical observables.

@@

\section{Estimating external convergence: The halo model approximation}
\label{sec:model}
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %

@@

\subsection{Correcting for voids, filaments and dark structures}
\label{subsec:voids}

@@

\section{Using the Millenium Simulation to test the halo model approximation with known halo mass and redshift}
\label{sec:knownMh+z}

In order to justify the reconstruction proceedure outlined in Section \ref{sec:model}, we would like to apply it to lines of sight with known $\kappa$. Because we want to test both accuracy and precision we need to know the true convergence for the line of sight. Since $\kappa$ isn't an observable we can not use real lines of sight but must use simulated lines of sight instead.

\subsection{Ray-tracing through simulated Lines of Sight}
\label{subsec:raytracing}
\todo{Stefan}{Write section on how the ray tracing was done}

\subsection{Generating mock lightcones from simulations}
\todo{Stefan}{Write section on how halos are extracted from the MS n-body particles}

>>>>

Every distant object we observe has had its apparent shape distorted,
and size and total brightness magnified (or demagnified) by a compound
weak gravitational lens constructed from all the mass distributed
between us and it. As \citet{Vale+White2003} and \citet{HilbertEtal2007}
showed, there are no empty lines of sight through our universe. This
fact makes gravitational lensing a potentially important source of
systematic error for any estimate of luminosity (or distance); this 
issue has been 
raised for \eg type Ia supernovae by
\citet[][]{Holz+Wald1998,Holz+Linder2005}, for gamma ray bursts by
\citet[][]{Oguri+Takahashi2006,Wang+Dai2011},  and for high redshift
galaxies by \citet{BradacEtal2009}, among others.

@@

Several attempts have been made to do better than simply constructing a
large sample of objects, and averaging over the resulting convergence
distribution. The weak lensing effect can be detected observationally 
by measuring the
small distortions it induces on the images of many background galaxies
in the field \citep[see e.g.][for a review]{SaasFee2006}. In a 30''
radius aperture around the strong lens Q0957$+$561,
\citet{NakajimaEtal2009} used deep HST imaging to measure a weak lensing
convergence of $0.17/pm0.06$, which was used in the time delay distance
measurement of \citep{FadelyEtal2009}. While this system has an
unusually high external convergence due to its location on the edge of a
cluster of galaxies, the precision with which the convergence at the
lens position can be estimated is indicative of what can be achieved
with high quality weak lensing shear data. We note that this uncertainty
is not dependent on the value of the convergence, but instead depends
primarily on the number density of weakly lensed, measurable galaxies
available.

@@

The probability density function (PDF) for the external convergence
given our available data $\data$, $\Pr(\xkappa|\data)$,  is the  key
quantity we seek, since by marginalising over this distribution we can
correctly propagate the uncertainties due to line-of-sight perturbations
(as \citeauthor{FadelyEtal2009} did).  
%
\citet{GunnarssonEtal2006} investigated a related PDF,  for the
magnification, using a galaxy halo model. Applying empirical galaxy
scaling relations both to simulate mock catalogs and then to reconstruct
the line of sight mass distribution. While they did not explore highly
overdense lines of sight, or the impact of groups and clusters, they
found that under their simplifying assumptions, the dispersion in
apparent source brightness due to lensing magnification could be reduced
by a factor of two.
%
\citet{WongEtal2011} estimated the PDF for the external shear,
$\Pr(\gamma|\data)$ from their survey data, running similar Monte Carlo
reconstructions of the mass in nine lens fields based on
\citeauthor{WilliamsEtal2006} and \citeauthor{MomchevaEtal2006}'s
photometric and spectroscopic measurements of galaxies close to the line
of sight. They then  compared the resulting predicted shear
distributions with the external shear demanded by the strong lens model.
Their reconstructions showed most of the shear to have been generated by
bright galaxies within 2~arcminutes of the lens, and that both line of
sight structures and the group of galaxies in each lens plane contribute
significant proportions of the shear. They found significant
discrepancies between the lens model shear and the Monte Carlo
predictions, but were unable to distinguish between the environment
modelling and the strong lens modelling as the cause of these
discrepancies.

These observational investigations have provided some very useful
insight into the problem of convergence estimation.  Coming from a more
theoretical direction, large numerical simulations have been used to
predict, from first principles, the distribution of likely external
shears and convergences along various lines of sight, including those
containing strong lens systems.  \citet{Holder+Schechter2003} and
\citet{DalalEtal2005} carried out ray-tracing calculations in N-body
simulations to estimate the distribution of external shear values. 
\citet{HilbertEtal2009} performed similar ray-tracing experiments
through the Millenium Simulation \citep{SpringelEtal2005}, generating a
predicted $\kappa$ at every position in a simulated sky.
\citet{HilbertEtal2009} found that \MS lines of sight with strong lenses
were not biased towards high $\kappa$, although selection functions for
discovering or using particular samples of strong lenses were not taken
into account. Addressing the possibility of using weak lensing shear to
reconstruct the magnification~$\mu$ that affects cosmography with
standard candles (and standard sirens), \citet{HilbertEtal2011} used the
\MS ray-tracing results to explore optimal mapping techniques and
quantify their performance. They found that deep weak lensing shear
surveys (with background galaxy number densities of 100 arcmin$^{-2}$)
would enable $\Pr(\mu|\data)$ to be estimated such that the distance
uncertainty per object would be reduced by  20\% on average, and by 40\%
in regions of low convergence, leading to the suggestion that weak
lensing maps be used to identify the (low convergence)  lines of sight
that give higher precision distance estimates.

The \MS results have been used to analyse real observations as well. 
\citet{SuyuEtal2010} selected \MS lines of sight by their apparent
galaxy overdensity, in a 45 arcsec radius aperture down to $i < 24.5$,
to match the observed overdensity towards the time delay lens
B1608$+$656 \citep{FassnachtEtal2011}.  The resulting distribution of
$\kappa$ values from the ray-tracing was taken to be an estimate of 
$\Pr(\kappa)$, which was then marginalised over when inferring the time
delay distance in this system. 
% B1608$+$656 is indeed a high $\kappa$
% line of sight, but it does not reside in a massive cluster environment.
In a companion paper to this one, \citet{GreeneEtal2012} investigated
improvements to this method by weighting the galaxy counts by galaxy
mass, and perpendicular distance to the line of sight, again using the
\MS mock catalogs and their associated $\kappa$ values to construct
$\Pr(\kappa|\data)$.

In this paper, we combine the halo model reconstruction approach of
\citeauthor{GunnarssonEtal2006} and \citeauthor{WongEtal2011}, with the
idea of calibrating to simulations from \citeauthor{SuyuEtal2009}, in
order to put the halo model for  estimating the weak lensing convergence
due to mass along the line of sight to a distant source into a sound
framework for evaluating this important source of systematic
uncertainty, as we look forward to ever increasing sample sizes and
statistical precision. Taking the $\kappa$ values from
\citeauthor{HilbertEtal2009}'s ray-tracing calculations as the ``truth''
that we have to recover, we use the \MS mock galaxy catalogs first to
{\it calibrate} the reconstruction, and account for unseen mass and
voids, and then to {\it test} the accuracy of the line of sight mass
reconstruction under this assumption. Probabilistically assigning mass
and redshift to every observed galaxy in a given observed field, we
generate Monte Carlo sample line of sight mass distributions, and so
construct the PDF $\Pr(\kappa|\data)$ for that field. We then emulate
the combination of many such PDFs to quantify the residual biases that
would be translated to the global (including cosmological) parameters.
In doing so, we aim to answer the following questions:

@@

\item We have some choices to make when planning follow-up observations
of interesting sightlines. How should we select objects to achieve the
highest accuracy convergence reconstruction? Can such a selection be
made robustly, using the reconstruction results?

@@

\begin{figure*}
\includegraphics[width=\textwidth]{figs/viewofalightcone.eps}
\caption[magcut]{Four different views of a slightly over-dense \MS line
of sight, with a $\kappa$ of 0.03. 
{\it Top row, left:} The positions of galaxies projected on the sky. The area
of the circles is proportional to observed $i$-band flux; the brightest
object shown has an $i$ magnitude of 17.7. 
{\it Top row, centre:} The angular sizes of halos projected on the sky.
Red and blue regions lie within the NFW scale radius and virial radius
of each halo, respectively. There are essentially no empty lightcones. 
{\it Top row, right:} The individual $\kappa$ contributions of
each halo, assuming the \citet{BMO} profile and the \citet{Neto2007}
mass-concentration relation. Comparison of
this panel and the centre panel reveals the relative importance of
proximity to the line of sight.
{\it Bottom:} A view along the redshift axis, showing only halos with
$|x|<0.3$ arcmin. The area of the points is proportional to each halo's
mass: the most massive halo shown has $1.6\times10^{12}\Msun$. The
optical axis is shown by the dashed line, while the dotted lines mark
the lens and source planes for a B1608-like strong lens.}
\label{fig:lightcone}
\end{figure*}

@@

Convergence, or Ricci focusing, occurs when a gravitational lens focuses
the rays in a given bundle. This focusing can cause distant objects to
appear brighter, and larger than they would if the lens were removed.
The convergence from an isolated mass sheet at a position
$\bmath{\theta}$ on the sky is the ratio of the projected surface
mass density ($\Sigma(D_{\mathrm{od}}\bmath{\theta})$) \devided by the
critical surface mass density at the redshift of the mass sheet
($\Sigma_{\rm cr}$),
\be
\kappa(\bmath{\theta})= \frac {\Sigma(D_{\mathrm{od}}\bmath{\theta})}
                              {\Sigma_{\rm cr}(\zd,\zs)}
\ee
where 
\be \label{eq:sigcrit} 
\Sigma_{\rm cr}(\zd,\zs) \equiv \frac{c^2 D_{\rm os}}{4 \pi G D_{\rm od} D_{\rm ds}}.
\ee
and the $D$'s are the angular diameter distances between the objects
refered to in the subscripts: o is the observer, d is the deflector and
s is the source. If the surface mass density of the sheet exceeds
$\Sigma_{\rm cr}$, multiple images of the source can occur, otherwise
only one image will be observed, although that image will still be
perturbed relative to the unlensed case.

@@

Strong lenses sit in our real Universe -- they are not \truely isolated;
there is some mass along the line of sight coming from intervening
structures. These structures may be physically associated with the lens
e.g. other members of a group or cluster, or they may be the result of
chance alignments at any redshift.  Whilst it is rare for three galaxies
to line up well enough for both of the background sources to be strongly
lensed \citep{GavazziEtal2008,CollettEtal2012a}, the large size of dark
matter halos makes a partial alignment -- with the additional structure
acting as a perturbing weak lens --  a near certainty
\citep{Vale+White2003,HilbertEtal2007}. These additional structures
induce an external shear which can be recovered in the mass-modelling of
the lens, but they can also introduce a convergence that is undetectable
from the image positions, shapes and relative fluxes
\citep{FalcoEtal1985}.

If the intrinsic source brightness changes, the observed brightness in
each image does not change simultaneously: there will be a time delay,
$\Delta t$, between the brightness change in each image. Despite the
invariance of the image positions and fluxes, under the addition of an
external convergence (and appropriate re-scaling of the lens potential)
the relative Fermat potential between the images is {\it not} invariant,
and so the time delay changes. As such it is necessary to include
$\kappa$ in the lens modelling, if cosmological parameters are to be
estimated accurately and precisely from observed time delays
\citep{SuyuEtal2010}. Mass distributions that are physically associated with the lens galaxy
will affect the stellar dynamics of the lens galaxy, so that dynamical
observations can break the internal mass-sheet degeneracy by providing
an additional estimate of the lens galaxy's mass
\citep[e.g.,][]{SuyuEtal2010}. In this work our aim is to quantify the
lensing effect of massive objects, regardless of their position along
the line of sight.

If there is external convergence present that is not included in the
lens modeling, then the time delay distance -- inferred assuming $\kappa
= 0$ -- will be $(1-\kappa)$ less than the true value of $\Dt$:
\be 
\label{eq:MassSheet:Dtbias}
\Dt^{\rm{true}}=(1-\kappa) \Dt^{{\kappax = 0}}.
\ee
We can hence estimate the true distance if we have  with additional
knowledge of $\kappa$. Since $\kappa$ is typically small the absolute
uncertainty on the estimate of $\kappa$ \correspends to the fractional
uncertainty with which time-delay distances can be \infered.

The relationship between convergence $\kappa$ and magnification $\mu$ is
\bea 
\mu &=&       \frac{1}{(1-\kappa)^2 - |\gamma|^2}, \notag \\
    &\approx& \frac{1}{(1-2\kappa)}
\label{eq:MassSheet:mag}
\eea
where we have used the fact that the magnitude of the gravitational
shear at any point is typically comparable to the magnitude of the 
convergence. For small $\kappa$, the fractional uncertainty in the
inferred luminosity of a magnified source will be approximately  twice
the absolute uncertainty in the convergence~$\kappa$. These
relationships will allow us to put our results on convergence estimation
in context.

@@

\section{The Millenium Simulation}
\label{sec:MS}

In order to test the accuracy of our convergence estimates, we need to
know the true convergence for each line of sight. We cannot use  real
lines of sight for this,  but must use simulated lines of sight instead.
In this section we briefly review the Millenium Simulation, the ray
tracing calculations that have been carried out in it, and the mock
galaxy catalogs that have been produced.

The \MS \citep{SpringelEtal2005} is a cosmological N-body simulation of
Dark Matter structures in a cubic region approximately 680~Mpc in
comoving size, followed from redshift 127 to the present day. With an
approximate halo mass resolution of $2\times10^{10}{\rm M}_{\odot}$
(corresponding approximately to a galaxy with luminosity $0.1L^{*}$), it
provides a detailed prediction for the distribution of dark structures
present in the Universe, under the assumptions of the $\Lambda$CDM model
of hierarchical structure formation, cosmological densities as given at
the end of \Sref{sec:intro}, and $\sigma_8 = 0.9$. 
Galaxy properties,
such as stellar masses, luminosities and colours, were assigned to the
simulated halos according to a semi-analytic model for galaxy formation
\citep{DeLucia+Blaizot2007}: the resulting predictions for the galaxy
luminosity function and correlation function match the observational
data very well.

\subsection{Convergence from Ray Tracing}
\label{sec:MS:raytracing}

\citet{HilbertEtal2009} calculated the lensing convergence using the
``lightcone'' dark matter only 
output of the \MS, providing 1.7 degree square 
mock sky maps of this
quantity. In this process, the dark matter density from the simulation
was projected onto a set of lens planes at discrete redshifts,
adaptively gridded and smoothed, and then the second derivatives of the 
lensing potential required for the components of the magnification
matrix were computed using a multiple lens plane ray tracing algorithm.
The first order approximation to this algorithm \citep[equation 17
of][]{HilbertEtal2009} gives the total convergence at a given sky
position~$\bmath{\theta}$ as the simple summation of the surface density
in each lens plane, weighted by the inverse critical surface density
$\Sigma_{\rm cr}$ for that plane's redshift:
\be
\kappa(\bmath{\theta}) = \sum_i \frac{\Sigma_i(\bmath{\theta})}
                                     {\Sigma_{\rm cr}(z_i,\zs)}.
\ee
This approximation was found to be accurate to a few percent or better
in $\kappa$, even on 30 arcsecond scales.

To define a test line of sight, we draw a random sky position from
within the convergence maps, bilinearly interpolate between the pixels
of the map, and store the result as the ``true'' convergence for that
line of sight, $\kappa_{\rm true}$.

\todo{Stefan}{Check this is all accurate and complete!}

\subsection{Mock Galaxy Catalogs}
\label{sec:MS:mocks}

Our goal is to recover the ``true'' convergence defined in the previous
sub-section, via an inference that takes a catalog of galaxy positions
and properties as data. We construct such catalogs by selecting all \MS
galaxies within a circular aperture of a given angular radius centred on
the line of sight position, with apparent $i$-band magnitude brighter
than a given limit. The parent catalog, from \citet{HilbertEtal2011},
contains galaxy positions and magnitudes, all of which include lensing
effects (deflections and magnifications). We also have access to the
underlying galaxy halo masses and redshifts, which we will use to
calibrate the reconstruction, and also to explore any sources of bias
and scatter. Since the true convergence is that of only the dark matter,
we focus on reconstructing the dark matter halos alone. Our model for
doing this is outlined in the next section.

\todo{Stefan, Tom}{Check this is all accurate and complete!}

\section{Estimating Convergence: The Halo Model Approximation}
\label{sec:model}

@@

\subsection{Accounting for voids, filaments and dark structures}
\label{subsec:voids}

@@

\section{Calibrating the halo model}
\label{sec:knownMh+z}

In order to test the reconstruction proceedure outlined in Section
\ref{sec:model}, we now apply it to mock galaxy catalogs generated in
regions on the sky around lines of sight with known
$\kappa$ in the Millenium Simulation.
